Squint: Lossy Hierarchical Compression on Symbol Streams

### 2012-12-10 tex/paper.tex
OMG typing in the results into the latex tables

\documentclass[11pt]{article}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array}
\usepackage{bm}
\usepackage{commath}
\usepackage{enumitem}
\usepackage{fancyhdr,fancyvrb}
\usepackage[letterpaper,text={7in,9in},centering]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage{ifthen}
\usepackage{mathrsfs}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{sectsty}
\usepackage{setspace}
\usepackage{stackrel}
\usepackage{stmaryrd}
\usepackage{tensor}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode}

@@

Below are the results on running Sequitur and Cluster, without
the grammar reductions, on the rep-n datasets. Time is the wall clock
running as measured on a 2.26 Ghz Intel Core 2 Duo Macbook Pro.
Ratio is the relative size of the grammar produced compared with
Sequitur, where the size of the grammar is the sum of the lengths of the
rhs's of the rules. Levdistance is the levenshtein distance between
the output of the lossified grammar and the original input string, it
is a kind of measure of the fidelity of our algorithms but doesn't
take into account how well patterns were preserved.

\begin{table}[h]
\begin{tabular}{l|l|l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
rep-100   & 0.006 & 18/34    & 0.713 & 0.002 & 20/34    & 0.535\\
rep-400   & 0.028 & 45/76    & 0.269 & 0.009 & 41/76    & 0.743\\
rep-1600  & 0.355 & 103/194  & 0.873 & 0.042 & 103/194  & 0.804\\
rep-6400  & 3.978 & 258/448  & 0.706 & 0.203 & 256/448  & 0.869\\
rep-12800 & & & & & & \\
rep-25600 & 135.0 & 900/1482 & 0.829 & 2.906 & 898/1482 & 0.725\\
\end{tabular}
\caption{rep-n: $\epsilon = .4$}
\end{table}

\begin{table}[h]
\begin{tabular}{l|l|l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
rep-100   & 0.002 & 30/34    & 0.040 & 0.002 & 30/34    & 0.040\\
rep-400   & 0.019 & 60/76    & 0.035 & 0.009 & 60/76    & 0.035\\
rep-1600  & 0.350 & 123/194  & 0.355 & 0.055 & 123/194  & 0.206\\
rep-6400  & 3.942 & 280/448  & 0.387 & 0.295 & 274/448  & 0.543\\
rep-12800 & & & & & & \\
rep-25600 & 124.5 & 922/1482 & 0.565 & 2.597 & 926/1482 & 0.437\\
\end{tabular}
\caption{rep-n: $\epsilon = .2$}
\end{table}

\begin{table}[h]
\begin{tabular}{l|l|l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
rep-100   & & /34    & & & /34    & \\
rep-400   & & /76    & & & /76    & \\
rep-1600  & & /194  & & & /194  & \\
rep-6400  & & /448  & & & /448  & \\
rep-12800 & & & & & & \\
rep-25600 & & /1482 & & & /1482 & \\
\end{tabular}
\caption{$rep-n: \epsilon = .1$}
\end{table}

TODO: Runtime graphs and regression. The exponents are about 1.8 and 1.3
respectively, note that the rulesize of sequitur grows at about sqrt(n)

Qualitatively the output strings generally are strings of a's with interspersed
`*' as expected, but the length of the final output varies widely.

Things to mention: Compression ratios and fidelity comparable for similarity
and cluster. Cluster has much better growth rate. Smaller epsilon provide
much better value/cost ratio as the input files get bigger for highly
repetitive files.

@@

\begin{table}[t]
\begin{tabular}{l|l|l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
gen-100   & & /& & & /& \\
gen-400   & & /& & & /& \\
gen-1600  & & /& & & /& \\
gen-6400  & & /& & & /& \\
gen-12800 & & /& & & /& \\
gen-25600 & & /& & & /& \\
\end{tabular}
\caption{$gen-n: \epsilon = .4$}
\end{table}

\begin{table}[t]
\begin{tabular}{l|l|l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
gen-100   & & /& & & /& \\
gen-400   & & /& & & /& \\
gen-1600  & & /& & & /& \\
gen-6400  & & /& & & /& \\
gen-12800 & & /& & & /& \\
gen-25600 & & /& & & /& \\
\end{tabular}
\caption{$gen-n: \epsilon = .2$}
\end{table}

\begin{table}[t]
\begin{tabular}{l|l|l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
gen-100   & & /& & & /& \\
gen-400   & & /& & & /& \\
gen-1600  & & /& & & /& \\
gen-6400  & & /& & & /& \\
gen-12800 & & /& & & /& \\
gen-25600 & & /& & & /& \\
\end{tabular}
\caption{$gen-n: \epsilon = .1$}
\end{table}

@@

\begin{table}[t]
\begin{tabular}{l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & C-T & C-R \\
\hline
rep-100   & & /& & /\\
rep-400   & & /& & /\\
rep-1600  & & /& & /\\
rep-6400  & & /& & /\\
rep-12800 & & /& & /\\
rep-25600 & & /& & /\\
\end{tabular}
\caption{$rep-n: \epsilon = .2$}
\end{table}

\begin{table}[t]
\begin{tabular}{l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & C-T & C-R \\
\hline
gen-100   & & /& & /\\
gen-400   & & /& & /\\
gen-1600  & & /& & /\\
gen-6400  & & /& & /\\
gen-12800 & & /& & /\\
gen-25600 & & /& & /\\
\end{tabular}
\caption{$gen-n: \epsilon = .2$}
\end{table}

>>>>

\documentclass[11pt]{article}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{array}
\usepackage{bm}
\usepackage{commath}
\usepackage{enumitem}
\usepackage{fancyhdr,fancyvrb}
\usepackage[letterpaper,text={7in,9in},centering]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage[lofdepth,lotdepth]{subfig}
\usepackage{ifthen}
\usepackage{mathrsfs}
\usepackage{multicol}
\usepackage{pifont}
\usepackage{sectsty}
\usepackage{setspace}
\usepackage{stackrel}
\usepackage{stmaryrd}
\usepackage{tensor}
\usepackage{xspace}
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode}

@@

Below are the results on running Sequitur and Cluster, without
the grammar reductions, on the rep-n datasets. Time is the wall clock
running as measured on a 2.26 Ghz Intel Core 2 Duo Macbook Pro.
Ratio is the relative size of the grammar produced compared with
Sequitur, where the size of the grammar is the sum of the lengths of the
rhs's of the rules. Levdistance is the levenshtein distance between
the output of the lossified grammar and the original input string, it
is a kind of measure of the fidelity of our algorithms but doesn't
take into account how well patterns were preserved. For the rep-n tests,
proportion is the proportion of the final string produced that was
`*'. The closer to 1/30~0.033, the more accurate the lossifier was
in recreating the original texture of the input.

The columns of the data are prefixed by S or T depending on whether
they are measurements for sequitur or cluster respectively.

\begin{table}[t]
\subfloat[$\epsilon = .4$]{
\begin{tabular}{l|l|l|l|l||l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & S-P(roportion) & C-T & C-R & C-L & C-P \\
\hline
rep-100   & 0.006 & 18/34    & 0.713 & 0.07 & 0.002 & 20/34    & 0.535 & 0.04\\
rep-400   & 0.028 & 45/76    & 0.269 & 0.01 & 0.009 & 41/76    & 0.743 & 0.04\\
rep-1600  & 0.355 & 103/194  & 0.873 & 0.03 & 0.042 & 103/194  & 0.804 & 0.02\\
rep-6400  & 3.978 & 258/448  & 0.706 & 0.005& 0.203 & 256/448  & 0.869 & 0.50\\
rep-12800 & 44.63 & 604/1064 & 0.791 & 0.01 & 1.136 & 600/1064 & 0.856 & 0.01\\
rep-25600 & 135.0 & 900/1482 & 0.829 & 0.005& 2.906 & 898/1482 & 0.725 & 0.25\\
\end{tabular}
}

\subfloat[$\epsilon = .2$]{
\begin{tabular}{l|l|l|l|l||l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & S-P(roportion) & C-T & C-R & C-L & C-P \\
\hline
rep-100   & 0.002 & 30/34    & 0.040 & 0.05 & 0.002 & 30/34    & 0.040 & 0.05\\
rep-400   & 0.019 & 60/76    & 0.035 & 0.02 & 0.009 & 60/76    & 0.035 & 0.02\\
rep-1600  & 0.350 & 123/194  & 0.355 & 0.03 & 0.055 & 123/194  & 0.206 & 0.01\\
rep-6400  & 3.942 & 280/448  & 0.387 & 0.08 & 0.295 & 274/448  & 0.543 & 0.09\\
rep-12800 & 42.21 & 638/1064 & 0.491 & 0.03 & 1.105 & 632/1064 & 0.457 & 0.01\\
rep-25600 & 124.5 & 922/1482 & 0.565 & 0.12 & 2.597 & 926/1482 & 0.437 & 0.007\\
\end{tabular}
}
\caption{rep-n Tests}
\end{table}

Runtime Comparison, esp. w.r.t num of rules.
Quality Comparison.
Epsilon Comparison.

@@

\begin{table}[t]
\subfloat[$\epsilon = .4$]{
\begin{tabular}{l|l|l|l||l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
gen-100   & 0.006 & 87/89    & 0.04 &0.006 & 87/89    & 0.04\\
gen-400   & 0.175 & 224/258  & 0.12 &0.069 & 219/258  & 0.19\\
gen-1600  & 4.863 & 539/697  & 0.31 &0.732 & 529/697  & 0.33\\
gen-6400  & 216.9 & 1740/2348& 0.41 &9.127 & 1694/2348& 0.43\\
gen-12800 & 1812  & 3296/4523& 0.40 &29.17 & 3181/4523& 0.44\\
gen-25600 & 12989 & 5823/8060& 0.43 &176.7 & 5540/8060& 0.50\\
\end{tabular}
}

\subfloat[$\epsilon = .2$]{
\begin{tabular}{l|l|l|l||l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
gen-100   & 0.004 & 89/89    & 0.00 &0.002 & 89/89    & 0.00 \\
gen-400   & 0.085 & 245/258  & 0.03 &0.053 & 245/258  & 0.03 \\
gen-1600  & 1.292 & 664/697  & 0.03 &0.874 & 664/697  & 0.03 \\
gen-6400  & 73.83 & 2173/2348& 0.05 &14.02 & 2171/2348& 0.05\\
gen-12800 & 549.2 & 4197/4253& 0.05 &45.64 & 4186/4253& 0.05\\
gen-25600 & 3939  & 7405/8060& 0.06 &224.9 & 7374/8060& 0.06\\
\end{tabular}
}
\caption{gen-n}
\end{table}

@@

\begin{table}[t]
\subfloat[rep-n tests]{
\begin{tabular}{l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & C-T & C-R \\
\hline
rep-100   & & /& & /\\
rep-400   & & /& & /\\
rep-1600  & & /& & /\\
rep-6400  & & /& & /\\
rep-12800 & & /& & /\\
\end{tabular}
}

\subfloat[gen-n tests]{
\begin{tabular}{l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & C-T & C-R \\
\hline
gen-100   & & /& & /\\
gen-400   & & /& & /\\
gen-1600  & & /& & /\\
gen-6400  & & /& & /\\
gen-12800 & & /& & /\\
\end{tabular}
}
\caption{Reducer Tests for $\epsilon = .2$}
\end{table}
